The state of knowledge for marine invertebrate biodiversity in the continental US

### 2017-11-06 manuscript.Rmd
remove xtable comment

```{r records-table, results='asis'}
print.xtableList(institution_contributions, colnames.format = "multiple",
                 booktabs = TRUE, include.rownames = FALSE,
                 table.placement = "!ht")
```

Marine invertebrates are underrepresented in iDigBio and OBIS given their diversity. We compared the total number of species represented in iDigBio and OBIS for each kingdom to the total described diversity based on the WoRMS estimates[@worms-stats]. Records in the databases are biased towards vertebrates: while vertebrates represent  `r total_vert_prop`% of the global diversity, they represent `r idigbio_vert_prop`% and `r obis_vert_prop`% of the species in iDigBio and OBIS respectively (Fig. \@ref(fig:kingdom-diversity-plot)). Additionally, the median number of specimens in iDigBio per species ranges between `r kng_medians %>% filter(sub_kingdom=="animalia") %>% pull(rg)` for invertebrate phyla, but is `r kng_medians %>% filter(sub_kingdom=="animalia - vertebrates") %>% pull(rg)` for vertebrates.

```{r kingdom-diversity-plot, fig.cap='Comparison of the proportions of the diversity represented in iDigBio and OBIS  with the global diversity (as reported by WoRMS) for each kingdom. Vertebrates are overrepresented, while other animal groups are underpresented. Total number of species are indicated next to the bars.(\\#fig:kingdom-diversity-plot)'}
knitr::include_graphics("figures/plot_kingdom_diversity.pdf")
```

>>>>

```{r records-table, results='asis'}
xtbl_small <- function(x) {
    glue::glue("{{\\footnotesize {x} }}")
}
xtbl_bold <- function(x) {
    glue::glue("{{\\bfseries {x} }}")
}
print.xtableList(institution_contributions, colnames.format = "multiple",
                 booktabs = TRUE, include.rownames = FALSE,
                 sanitize.subheadings.function = xtbl_bold, 
                 sanitize.message.function = xtbl_small, 
                 table.placement = "!ht", comment = FALSE)
```

Marine invertebrates are underrepresented in iDigBio and OBIS given their diversity. We compared the total number of species represented in iDigBio and OBIS for each kingdom to the total described diversity based on the WoRMS estimates[@worms-stats]. While marine vertebrates represent  `r total_vert_prop`% of the global diversity, they represent `r idigbio_vert_prop`% and `r obis_vert_prop`% of the species in iDigBio and OBIS respectively (Fig. \@ref(fig:kingdom-diversity-plot)). Additionally, the median number of specimens in iDigBio per species ranges between `r kng_medians %>% filter(sub_kingdom=="animalia") %>% pull(rg)` for invertebrate phyla, but is `r kng_medians %>% filter(sub_kingdom=="animalia - vertebrates") %>% pull(rg)` for vertebrates.

<!-- find checklists for fish, birds, mammals to compare with -->

```{r kingdom-diversity-plot, fig.cap='Comparison of the proportions of the diversity represented in iDigBio and OBIS  with the global diversity (as reported by WoRMS) for each kingdom. Vertebrates are overrepresented, while other animal groups are underpresented. Total number of species for each category are indicated next to the bars.(\\#fig:kingdom-diversity-plot)'}
knitr::include_graphics("figures/plot_kingdom_diversity.pdf")
```
